
\documentclass{muratcan_cv}

\setname{Jordan Ayala}{}
\setaddress{Asunción, Paraguay}
\setmobile{+595 991-171-554}
\setmail{jor.ayalag@gmail.com}
% \setmail{jordan@jordanbuilds.io}
% \setcitizenship{Eldian Citizen}
\setlinkedinaccount{https://www.linkedin.com/in/jordan-ayala/} 
\setgithubaccount{https://github.com/jmayalag} 
\setthemecolor{RoyalBlue}

    
\begin{document}
\headerview
\vspace{1ex} % white space
\section{Experience}
%
\datedexperience{Technical Lead}{Feb 2022 - Mar 2024}
\explanation{BairesDev}{San Francisco, California, United States, Remote}
\explanationdetail{
\smallskip
\coloredbullet\ %
Led a team of 10 talented engineers in building a platform that handles the operation of several warehouses across the US (Kotlin, NestJs, Typescript, Javascript, React).

\smallskip
\coloredbullet\ %
 Consolidated multiple data sources to Google Big Query Platform allowing efficient analytical and operational reporting, leading to a 60% reduction in response times.

\smallskip
\coloredbullet\ %
 Built real-time streaming applications (Kafka, Kotlin) that integrated various microservices and multiple warehouse providers, ensuring seamless operational functionality and efficiency.

\smallskip
\coloredbullet\ %
 Mentored a team of engineers, providing guidance and expertise in software architecture enhancement and optimization.

\smallskip
}
%
\datedexperience{Lead Mobile Engineer}{Mar 2019 - Feb 2022}
\explanation{Luke's Local}{San Francisco Bay Area, Remote}
\explanationdetail{
\smallskip
\coloredbullet\ %
Led the development of an online food ordering application (iOS & Android) focusing on enhancing user experience and operational efficiency (React Native, Typescript, Redux).

\smallskip
\coloredbullet\ %
 Integrated advanced analytics into the application, enabling data-driven strategies to track and improve user satisfaction using Firebase and Mixpanel.

\smallskip
\coloredbullet\ %
 Led the development of a successful referral program that encouraged user engagement and growth.

\smallskip
\coloredbullet\ %
 Innovated by designing and implementing a companion application to efficiently track inbound supplies, streamlining the supply chain process.

\smallskip
}
%
\datedexperience{Senior Mobile Engineer}{Apr 2021 - Jan 2022}
\explanation{Voice}{United States, Remote}
\explanationdetail{
\smallskip
\coloredbullet\ %
Built the application for an NFT marketplace that is carbon neutral, easy to use on the EOS blockchain serving over 10.000 customers (Android, Kotlin, MVVM, OOP).

\smallskip
\coloredbullet\ %
 Led the development the authentication infrastructure.

\smallskip
\coloredbullet\ %
 Led the integration of KYC services, significantly reducing the number of bot accounts.

\smallskip
\coloredbullet\ %
 Designed and implemented the NFT multimedia viewer.

\smallskip
}
%
\datedexperience{Data Scientist}{Jun 2020 - Sep 2021}
\explanation{Universidad Americana Paraguay}{Asunción, Paraguay, Hybrid}
\explanationdetail{
\smallskip
\coloredbullet\ %
Contributed to the creation of a platform to assist a team of experts in the early diagnosis of diabetic retinopathy (Keras, Python, NextJS).

\smallskip
\coloredbullet\ %
 Led the research multiple state-of-the-art algorithms for object detection and designed experiments to train and validate machine learning models.

\smallskip
\coloredbullet\ %
 Built a machine learning classification model with eye fundus images.

\smallskip
\coloredbullet\ %
 Built a REST API to provide diabetic retinopathy detection (Python, FastAPI, Keras).

\smallskip
}
%
\datedexperience{Android Team Lead}{Sep 2019 - Mar 2021}
\explanation{SweatWorks}{Washington, United States, Remote}
\explanationdetail{
\smallskip
\coloredbullet\ %
Led a team of Android and QA Engineers in building and launching a fitness app offering on-demand workout classes like cycling, yoga, and strength training (Android, Kotlin).

\smallskip
\coloredbullet\ %
 Built integrations with Bluetooth powered devices to track the workout performance of users.

\smallskip
\coloredbullet\ %
 Integrated multiple streaming platforms to improve the user experience during workouts. (Mux, FeedFM)

\smallskip
\coloredbullet\ %
 Built a Proof of concept App for Android TV.

\smallskip
}\section{Education}
%
\datedexperience{Engineer's degree - Computer Software Engineering}{2012 - 2016}
\explanation{Universidad Nacional de Asunción}{} 
\explanationdetail{
\smallskip
\coloredbullet\ %
 Received Full Tuition Scholarship for academic merit.

\smallskip
\coloredbullet\ %
 Thesis on intelligent stock market trading systems was published on a major scientific journal.

\smallskip
}\section{Publications}
%
\explanationdetail{
\smallskip 
\textbf{Jordan Ayala} and \textbf{Miguel García}, "Technical analysis strategy optimization using a machine learning approach in stock market indices," \emph{2021 Elsevier}, Knowledge Based Systems.
}
%
\section{Skills}
\explanationdetail{
\smallskip 
Strategic planning; warehouse logistics; package logistics; stakeholder communication; technical leadership; scrum; e-commerce; Python; Kotlin; Java; JavaScript; TypeScript; GoLang; Rust; SQL; Shopify; Kafka; AWS; GCP; Tensorflow; Machine Learning; React Native; React; Next.js; Spring; MySql; Redis; Mongo
}
\end{document}
